\section{Introduction}
This user manual is intended for the Administrators (Executive Committee) and Advisors of the Science Club. It guides users through the common operations of the CPMS.

\section{Administration Guide}

\subsection{Getting Started}
\begin{enumerate}
    \item \textbf{URL:} Navigate to \url{https://mbstusc.eksofts.xyz/login}
    \item \textbf{Login:} Enter your admin email and password.
    \item \textbf{Dashboard:} You will be greeted by the statistics panel.
\end{enumerate}

\subsection{Managing Members}
To add a new Exeuctice Committee member:
\begin{enumerate}
    \item Click on **"Manage Team"** in the left sidebar.
    \item Click the **"Add New Member"** button (top right).
    \item Fill in the form:
    \begin{itemize}
        \item \textbf{Name:} Full Name
        \item \textbf{Designation:} e.g. "General Secretary"
        \item \textbf{Image:} Click browse and select a 500x500px JPG.
    \end{itemize}
    \item Click **Save**. The member is now visible on the public "Team" page.
\end{enumerate}

\subsection{Designing a Certificate}
\begin{enumerate}
    \item Navigate to **"Templates"**.
    \item Click **"Create Template"**.
    \item Upload your blank certificate design (ensure it has high resolution).
    \item On the canvas, you will see draggable boxes: "Name", "Date", "Reg ID".
    \item Drag them to the lines on your certificate background.
    \item Click **"Save Template"**.
\end{enumerate}

\section{Advisor Guide}

\subsection{Approving Certificates}
You do not need to check the website daily. You will receive an email when a verification is needed.

\begin{enumerate}
    \item \textbf{Open Email:} Look for subject "Action Required: Certificate Verification".
    \item \textbf{Click Link:} Click the "Review Application" button in the email body.
    \item \textbf{Login:} If not logged in, enter your credentials.
    \item \textbf{Review:} You will see the student's details and impact statement.
    \item \textbf{Action:}
    \begin{itemize}
        \item \textbf{Approve:} Digitally signs and emails the student.
        \item \textbf{Decline:} Requires you to write a note explaining why (e.g. "Not a member").
    \end{itemize}
\end{enumerate}

\section{Troubleshooting}

\subsection{Common Issues}
\begin{itemize}
    \item \textbf{Issue:} Email not received.
    \item \textbf{Fix:} Check Spam folder. If using a university mail server, ensure firewall allows external mails.
    
    \item \textbf{Issue:} "419 Page Expired" Error.
    \item \textbf{Fix:} Refresh the page. Your CSRF token expired because the page was open too long.
    
    \item \textbf{Issue:} Image upload fails.
    \item \textbf{Fix:} Ensure image is under 2MB.
\end{itemize}
