\chapter{System Analysis}
\label{chap:system_analysis}

\section{User Roles and Permissions}
The system is designed for three distinct types of users, each with specific permissions and interfaces.

\subsection{Administrator (Executive Committee)}
The Admin has the highest level of control. Responsibilities include:
\begin{enumerate}
    \item \textbf{Content Management:} Updating "About Us", "Mission/Vision", "FAQs", and "Gallery" sections.
    \item \textbf{Team Management:} Adding or removing Executive Committee members and regular members.
    \item \textbf{Certificate Management:} designing templates, setting text positions, and initiating the certificate approval process.
    \item \textbf{Settings:} Configuring website-wide settings like contact emails, social links, and current President signatures.
\end{enumerate}

\subsection{Advisor (Faculty)}
Advisors are professors or faculty members. Their role is streamlined to respect their time:
\begin{enumerate}
    \item \textbf{Approval:} Reviewing certificate applications forwarded by the admin.
    \item \textbf{Authentication:} Secure login via shared credentials to a simplified dashboard.
    \item \textbf{Action:} A single-click approval mechanism that triggers the final email to the applicant.
\end{enumerate}

\subsection{Applicant/Visitor}
General users or club members who interact with the public face of the website.
\begin{enumerate}
    \item \textbf{Application:} Applying for certificates by submitting details (Impact, Membership dates).
    \item \textbf{Tracking:} Monitoring the status of their application (Pending, Verified, Approved, or Declined).
    \item \textbf{Verification:} Verifying the authenticity of a certificate using the track ID.
\end{enumerate}

\section{Functional Requirements}

\subsection{Certificate Ticketing System}
This is the core feature. The workflow is as follows:
\begin{itemize}
    \item A member submits an application via the website.
    \item Admin receives an email notification.
    \item Admin logs in, verifies the claim, and selects an appropriate template.
    \item Admin "Verifies" the application. This sends an email to the designated Advisor.
    \item The Advisor receives the email, logs in, and "Approves" the certificate.
    \item The system automatically generates the final image/PDF with all signatures and emails it to the applicant.
\end{itemize}

\subsection{Template Designer}
The admin panel must include a canvas-based editor (utilizing Fabric.js or similar logic) where admins can:
\begin{itemize}
    \item Upload background images.
    \item Add text placeholders (Name, Certificate Text, Date).
    \item Drag and drop elements to position them correctly.
    \item Save the layout as a persistent template for future use.
\end{itemize}

\subsection{Security Mechanisms}
\begin{itemize}
    \item \textbf{OTP Verification:} Critical actions like changing the admin email/password or sending contact emails require One-Time Password verification.
    \item \textbf{Deep Web Dashboard:} The admin dashboard is secured and not indexed, providing a "Deep Web" layer of security.
\end{itemize}

\section{Non-Functional Requirements}
\begin{itemize}
    \item \textbf{Responsiveness:} The UI must adapt to mobile, tablet, and desktop screens.
    \item \textbf{Performance:} Fast load times using Inertia.js and optimized assets.
    \item \textbf{Data Integrity:} Reliable storage of member data and certificate records using SQLite (for this implementation).
\end{itemize}
