\chapter{Conclusion and Future Work}
\label{chap:conclusion}

\section{Conclusion}
The Science Club Management System successfully digitizes the manual operations of the MBSTU Science Club. By implementing a sophisticated certificate ticketing system, the project addresses the core challenge of authentic verification and streamlined issuance. The use of a "Modern Tech Stack" (Laravel 12, Vue 3, Inertia, Tailwind 4) ensures the application is future-proof, secure, and visually appealing. The separation of concerns between the Admin and Advisor panels respects the hierarchy and workflow of a university organization.

\section{Limitations}
\begin{itemize}
    \item \textbf{Offline Access:} The system currently requires an active internet connection; there is no offline mode for the admin panel.
    \item \textbf{Database:} SQLite is used for simplicity but may face scaling issues if the application is deployed for multiple clubs simultaneously.
\end{itemize}

\section{Future Work}
\begin{itemize}
    \item \textbf{Multi-Tenancy:} Expanding the SaaS model to support multiple clubs from other universities on the same platform.
    \item \textbf{PWA Support:} Converting the frontend into a Progressive Web App for better mobile installation.
    \item \textbf{AdSense Integration:} As mentioned in the requirements, integrating Google AdSense on high-traffic pages (like results) to generate revenue for the club.
    \item \textbf{Alumni Network:} Adding a specific module for alumni to stay connected and donate to the club.
\end{itemize}
